Optimized and Cost Considering Huffman Code For Biological Data Transmission

### 2015-01-24 Article/Article.tex
expre

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{lscape}
\usepackage[noend]{algpseudocode}
\usepackage{algcompatible}

@@

\section{Approach}
\label{sec3}
\subsection{Proposed Scheme}

\begin{figure}[thpb]
\begin{center}

\includegraphics[scale=0.5]{Images/Drawing3.jpg}
\caption{The proposed Scheme}
\end{center}
\label{Fig1}
\end{figure}

@@

\begin{figure}[thpb]
\begin{center}

\includegraphics[scale=0.7]{Images/Drawing1.jpg}
\caption{Population Update for genetic algorithm}
\end{center}
\label{Fig2}
\end{figure}

\begin{figure}[h]
\begin{center}

\includegraphics[scale=0.5]{Images/Drawing2.jpg}
\caption{Operations of genetic algorithm}
\end{center}
\label{Fig3}
\end{figure}

\section{Results And Discussion}

\begin{table}
\small
\label{datas}
\caption{}
\begin{center}
\begin{tabular}{c  c  c}
\toprule
$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size}$ \\\hline
Data set 1& Mycobacterium smegmatis & \\\hline
Data set 2& Amycolatopsis benzoatilytica &\\\hline
Data set 3& Mycobacterium rhodesiae& \\\hline
Data set 4& Streptomyces bottropensis& \\\hline
Data set 5& Mycobacterium smegmatis. MC2& \\\hline
Data set 6& Mycobacterium smegmatis MKD8& \\\hline
Data set 7& Bradyrhizobium WSM471& \\\hline
Data set 8& Amycolatopsis thermoflava& \\\hline
Data set 9& Bacillus thuringiensis serovar thuringiensis& \\\hline
Data sets 10& Bacillus thuringiensis Bt407& \\\hline
Data set 11& Pseudomonas aeruginosa 9BR& \\\hline
Data set 12& Bacillus thuringiensis serovar berliner& \\\hline
Data set 13& Bacillus thuringiensis serovar pakistani&\\\hline
Data set 14& Pseudomonas aeruginosa LES400&\\\hline
\bottomrule
\end{tabular}
\end{center}
\end{table}

\begin{table}
\small
\label{datas}
\caption{GABM for comparison for cost and number of bits of different approaches with different datasets}
\begin{center}
\begin{tabular}{c | c c | c c | c c}
\toprule
$\textbf{Data sets}$ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA}\\\hline
 & $\textbf{Cost}$	& $\textbf{Bits}$ &	$\textbf{Cost}$&	$\textbf{Bits	}$&$\textbf{Cost}$&	$\textbf{Bits}$
\\\hline
Data set 1&76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
Data set 2&100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
Data set 3&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
Data set 4&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
Data set 5&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
Data set 6&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
Data set 7&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
Data set 8&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
Data set 9&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
Data set 10&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
Data set 11&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
Data set 12&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
Data set 13&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
Data set 14&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[h]
\begin{center}

\includegraphics{Images/Drawing4.jpg}
\caption{Convergence of Optimized cost considering Huffman algorithm}
\end{center}
\label{Fig5}
\end{figure}
\section{Conclusion}
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{lscape}
\usepackage[noend]{algpseudocode}
\usepackage{algcompatible}
\usepackage{multirow}

@@

\section{Approach}
\label{sec3}
\subsection{Proposed Scheme}
A gene is a stretch of DNA (or RNA) that codes for a polypeptide (protein), that is a series of aminoacids bound together. Each gene consists of nucleotides bound together, which are interpreted by the cellular machinery in groups of three, called triplets. DNA is first transcribed into messenger RNA (mRNA), which is then translated into proteins. Each triplet codes for one aminoacid not one gene! In fact genes are not "coded" by anything, they are the code!

\begin{figure}[thpb]
\begin{center}
\includegraphics[scale=0.5]{Images/Drawing3.jpg}
\caption{The proposed Scheme}
\end{center}
\label{Fig1}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.7]{Images/Drawing1.jpg}
\caption{Population Update for genetic algorithm}
\end{center}
\label{Fig2}
\end{figure}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.5]{Images/Drawing2.jpg}
\caption{Operations of genetic algorithm}
\end{center}
\label{Fig3}
\end{figure}

\section{Results And Discussion}
The approach has been evaluated with different real biological data (genomes), these genomes from The National Center for Biotechnology Information (NCBI) available on ( http://www.ncbi.nlm.nih.gov) []. In table () the different data set are described with the size of each of them and the references on the biological data bank.
\begin{table}
\small
\label{datas}
\caption{Dataset description}
\begin{center}
\begin{tabular}{c  c  c c}
\toprule
$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (bp)}$ &	$\textbf{Reference}$ \\\hline
Genome 1& Mycobacterium smegmatis &6,988,302 & CP009496  \\\hline

Genome 2& Amycolatopsis benzoatilytica &  8,704,271& NZ\_KB912942 \\\hline

\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6,415,739} & \multirow{2} {*}{CP003169}\\ 
&NBB3& &\\
\hline

\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8,955,726} &
\multirow{2}{*}{NZ\_KB911581} \\ 
& ATCC 25435 \\
\hline

\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{6,988,269 } &\multirow{2}{*}{CP009494             } \\ 
&str. MC2 155 \\
\hline

\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{7,092,137} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
\hline

Genome 7& Bradyrhizobium WSM471& 7,784,016  &NZ\_CM001442\\\hline

\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8,677,910} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
\hline

\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{6,026,843} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
\hline

\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6,323,123 } &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
\hline

\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6,801,503  } &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
\hline

\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{6,260,142  } &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
\hline

\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{6,037,513 } &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
\hline

\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6,591,121  } &\multirow{2}{*}{ CP006982  }\\    &LES400&\\
\hline
\bottomrule
\end{tabular}
\end{center}
\end{table}

T

\begin{table}
\small
\label{datas}
\caption{GABM for comparison for cost and number of bits of different approaches with different datasets}
\begin{center}
\begin{tabular}{c | c c | c c | c c}
\toprule
$\textbf{Data sets}$ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA}\\\hline
 & $\textbf{Cost}$	& $\textbf{Bits}$ &	$\textbf{Cost}$&	$\textbf{Bits	}$&$\textbf{Cost}$&	$\textbf{Bits}$
\\\hline
Genome 1&76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
Genome 2&100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
Genome 3&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
Genome 4&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
Genome 5&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
Genome 6&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
Genome 7&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
Genome 8&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
Genome 9&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
Genome 10&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
Genome 11&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
Genome 12&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
Genome 13&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
Genome 14&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[h]
\begin{center}
\includegraphics{Images/Drawing4.jpg}
\caption{Convergence of Optimized cost considering Huffman algorithm}
\end{center}
\label{Fig5}
\end{figure}
\section{Conclusion}
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix
